R Packages to Aid in Handling Web Access Logs

### 2016-01-02 paper/paper.Rmd
Update paper.Rmd
typo: missing space to_include

### Decoding
Both values can be percent-encoded, allowing them toinclude characters that are valid but reserved by the URL specification as having special meanings ("reserved characters"). A \samp{\#} symbol, for example, is encoded as \samp{\%23}: a percentage symbol, followed by the byte-code for that character.

>>>>

### Decoding
Both values can be percent-encoded, allowing them to include characters that are valid but reserved by the URL specification as having special meanings ("reserved characters"). A \samp{\#} symbol, for example, is encoded as \samp{\%23}: a percentage symbol, followed by the byte-code for that character.
